### 2018-04-26 doc/paper.tex
Adding page / context to the three included quotes.

From \cite{Delgado2015}

@@

\noindent In the same paper (when referring to \cite{Bezerra2013}):

@@

\noindent From the same author, in \cite{Mainar2005}:

>>>>

From \cite{Delgado2015} (end of Section 3):

@@

\noindent In the same paper (when referring to \cite{Bezerra2013} at the
beginning of Section 2):

@@

\noindent From the same author, in \cite{Mainar2005} (towards the
end of Section 5, at the bottom of page 109):
